A Wait-free Queue with Poly-logarithmic Step Complexity

### 2022-12-18 podc_paper/related.tex
Edited related work on fetch&inc

\paragraph{Universal Constructions}
One can also build a queue using a universal construction \cite{10.1145/114005.102808}.
Jayanti \cite{DBLP:conf/podc/Jayanti98a} observed that
the universal construction of Afek, Dauber, and
Touitou~\cite{DBLP:conf/stoc/AfekDT95} can be modified to use $O(\log p)$ steps per operation, 
using atomic access to $\Omega(p \log p)$-bit words. 
(Thus, in terms of operations on reasonably-sized words, their construction would still take $\Omega(p)$ steps per operation.)
Fatourou and Kallimanis \cite{FK14} used their universal construction based on fetch\&add and LL/SC instructions
to implement a queue, but its step complexity is also $\Omega(P)$.
\here{Double check this.}

@@

\paragraph{Fetch\&Increment Objects}
Ellen and Woelfel introduced an implementation of a Fetch\&Increment object
with step complexity of $O(\log p)$ using $O(\log n$)-bit
\texttt{LL/SC} objects, where $n$ is the number of
operations~\cite{10.1007/978-3-642-41527-2_20}. Their idea to achieve
logarithmic complexity is to use a tree storing the Fetch\&Increment
operations invoked by processes. When a process wants to do a
Fetch\&Increment it adds its Fetch\&Increment to the tree and returns the number
of elements in the tree. There are some similarities between designing
a queue and a Fetch\&Increment object. A Fetch\&Increment object can be
constructed from a queue. The algorithm by Ellen and Woelfel is
interesting because of the similarities between Fetch\&Increment objects and
queues. Also, it is one of the few wait-free data structures achieving
poly-logarithmic complexity.

>>>>

\paragraph{Universal Constructions}
One can also build a queue using a universal construction \cite{10.1145/114005.102808}.
Jayanti \cite{DBLP:conf/podc/Jayanti98a} observed that
the universal construction of Afek, Dauber, and
Touitou~\cite{DBLP:conf/stoc/AfekDT95} can be modified to use $O(\log p)$ steps per operation, 
assuming that words can store $\Omega(p \log p)$ bits. 
(Thus, in terms of operations on reasonably-sized $O(\log p)$-bit words, their construction would take $\Omega(p\log p)$ steps per operation.)
Fatourou and Kallimanis \cite{FK14} used their universal construction based on fetch\&add and LL/SC instructions
to implement a queue, but its step complexity is also $\Omega(P)$.
\here{Double check this.}

@@

\paragraph{Fetch\&Increment Objects}
Progress has been made on obtaining sublinear-time implementations of other objects 
with consensus number 2.
Two papers \cite{ERW12,10.1007/978-3-642-41527-2_20}
implemented fetch\&increment objects from LL/SC objects
using a polylogarithmic number of steps per operation.
Our approach is similar to that of Ellen, Ramachandran and Woelfel \cite{ERW12},
which uses a tournament tree to keep track of the fetch\&increment operations
that have been performed.  However, our construction requires much more intricate
data structures, since the state of a queue cannot easily be represented as succinctly
as the single-word state of a fetch\&increment object.
